---
title: "Error rate of permutation and bootstrap methods"
author: "John Flournoy"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r eval = FALSE, echo = FALSE}
permediatr::generate_slurm_file(bash_out_dir = '../inst/bin/', 
                                nreps = 500, niter = 2500, mc.cores = 24,
                                simtype = 'bootstrap',
                                J = 100, n_j = 10,
                                a = c(0, .2, .8),
                                b = c(0, .2, .8),
                                c_p = c(0, .8),
                                theta_ab = .2,
                                re.form = c('NA'), 
                                boottype = 'parametric', 
                                optimizer = 'bobyqa',
                                job_name = 'bootmediatr',
                                job_time = '3-00:00:00',
                                job_mem = '10G', 
                                partition = 'ncf_holy', 
                                email_address = 'john_flournoy@fas.harvard.edu', 
                                save_dir = '/net/holynfs01/srv/export/mclaughlin/share_root/users/jflournoy/data/boot',
                                fname_prefix = 'boot_NA_par')
```

The output from the simulations needs to be collected first from the csv output. Another aspect of the output is that each simulation gives the p-value of the indirect path as just the cumulative probability. We want to reject the null for any indirect path where that is either < .025 or > .975. I'll summarize the output to look at the error rate (any null rejection) for each subset of simulation input (a path, b path, and c_p path). There are three ways I could imagine getting a p-value from the permutation-generated confidence interval -- first, subtracting the mean of all permutations, to center the CI around 0, `p_ab_perm_mean_c`; second, centering that distribution around the model-estimated a*b path, `p_ab_perm_ab_c`; and third, taking the proportion of the CI that is below 0. In the final case, to keep the test two-sided, we reject the null when > .025 proportion of the tail is of the sign opposite the indirect effect estimate.

```{r}
library(permediatr)
library(data.table)
library(ggplot2)
proportion_fp <- function(p, alpha = .05) {
  left <- alpha/2
  right <- 1 - alpha/2
  p_fp <- mean(p < left) + mean(p > right)
  p_se <- sqrt( (p_fp * (1 - p_fp)) / length(p) )
  u.975 <- p_fp + 1.96 * p_se
  l.025 <- p_fp - 1.96 * p_se
  return(list(p_fp = p_fp, l.025 = l.025, u.975 = u.975))
}
bias_ci <- function(v){
  bias <- mean(v)
  se <- sd(v)/sqrt(length(v))
  u <- bias + 1.96*se
  l <- bias - 1.96*se
  return(list(bias = bias, l.025 = l, u.975 = u))
}
perm_file_list <- dir(system.file('csv', package = 'permediatr'), 
                      pattern = 'pmjob.*csv', full.names = TRUE)
perm_sim_results <- data.table::rbindlist(lapply(perm_file_list, data.table::fread), fill = TRUE)
set(perm_sim_results, i = which(is.na(perm_sim_results[['permtype']])), j = 'permtype', 'within')
perm_sim_results[, a_or_b_size := pmax(a,b)]
perm_sim_bias_summary <- perm_sim_results[, bias_ci(ab - mean_ab_perm),
                                          by = .(a_or_b_size, c_p, reform, permtype)]
perm_sim_results_l <- data.table::melt(perm_sim_results, 
                                       id.vars = c('a_or_b_size', 'c_p', 'reform', 'permtype'),
                                       measure.vars = grep('p_', names(perm_sim_results), value = T), 
                                       value.name = 'p')
perm_sim_results_summary_l <- perm_sim_results_l[, 
                                                 proportion_fp(p), 
                                                 by = .(variable, a_or_b_size, c_p, reform, permtype)]
```

# Permutation Sim Results {.tabset}

## NULL within

```{r fig.width = 7, fig.height = 5}
ggplot(perm_sim_results_summary_l[reform == 'NULL' & permtype == 'within'], 
       aes(x = a_or_b_size, y = p_fp, group = c_p)) +
  geom_hline(yintercept = .05, linetype = 'dotted') +
  geom_line(alpha = .5) +
  geom_linerange(aes(ymin = l.025, ymax = u.975)) + 
  geom_point(aes(shape = factor(c_p)), alpha = .5, size = 2) + 
  scale_y_continuous(breaks = c(.05, .5, 1)) +
  facet_wrap(~variable) +
  coord_cartesian(ylim = c(0,1)) +
  theme_minimal() +
  labs(title = 'reform = NULL, permutations = within',
       x = 'Size of largest non-zero path (a or b)',
       y = 'Proportion false positive\n(95% CI)')
```

## NA within

```{r fig.width = 7, fig.height = 5}
ggplot(perm_sim_results_summary_l[is.na(reform) & permtype == 'within'], 
       aes(x = a_or_b_size, y = p_fp, group = c_p)) +
  geom_hline(yintercept = .05, linetype = 'dotted') +
  geom_line(alpha = .5) +
  geom_linerange(aes(ymin = l.025, ymax = u.975)) + 
  geom_point(aes(shape = factor(c_p)), alpha = .5, size = 2) + 
  scale_y_continuous(breaks = c(.05, .5, 1)) +
  facet_wrap(~variable) +
  coord_cartesian(ylim = c(0,1)) +
  theme_minimal() +
  labs(title = 'reform = NA, permutations = within',
       x = 'Size of largest non-zero path (a or b)',
       y = 'Proportion false positive\n(95% CI)')
```

## NA bw/within

```{r fig.width = 7, fig.height = 5}
ggplot(perm_sim_results_summary_l[is.na(reform) & permtype == 'between_within'], 
       aes(x = a_or_b_size, y = p_fp, group = c_p)) +
  geom_hline(yintercept = .05, linetype = 'dotted') +
  geom_line(alpha = .5) +
  geom_linerange(aes(ymin = l.025, ymax = u.975)) + 
  geom_point(aes(shape = factor(c_p)), alpha = .5, size = 2) + 
  scale_y_continuous(breaks = c(.05, .5, 1)) +
  facet_wrap(~variable) +
  coord_cartesian(ylim = c(0,1)) +
  theme_minimal() +
  labs(title = 'reform = NA, permutations = betwee_within',
       x = 'Size of largest non-zero path (a or b)',
       y = 'Proportion false positive\n(95% CI)')
```

## Table of FPs

```{r}
knitr::kable(perm_sim_results_summary_l)
```

## Table of Bias

```{r}
knitr::kable(perm_sim_bias_summary)
```

# Bootstrap Sim Results {.tabset}

```{r}
boot_file_list <- dir(system.file('csv', package = 'permediatr'), 
                      pattern = 'boot.*csv', full.names = TRUE)
boot_sim_results <- data.table::rbindlist(lapply(boot_file_list, data.table::fread), fill = TRUE)
boot_sim_results[, a_or_b_size := pmax(a,b)]
boot_sim_bias_summary <- boot_sim_results[, bias_ci(ab - boot_ab),
                                          by = .(a_or_b_size, c_p, reform, boottype)]
boot_sim_results_l <- data.table::melt(boot_sim_results, 
                                       id.vars = c('a_or_b_size', 'c_p', 'reform', 'boottype'),
                                       measure.vars = grep('p_', names(boot_sim_results), value = T), 
                                       value.name = 'p')
boot_sim_results_summary_l <- 
  boot_sim_results_l[, proportion_fp(p), 
              by = .(variable, a_or_b_size, c_p, reform, boottype)]
```

## NA parametric

```{r fig.width = 7, fig.height = 5}
ggplot(boot_sim_results_summary_l, 
       aes(x = a_or_b_size, y = p_fp, group = c_p)) +
  geom_hline(yintercept = .05, linetype = 'dotted') +
  geom_line(alpha = .5) +
  geom_linerange(aes(ymin = l.025, ymax = u.975)) + 
  geom_point(aes(shape = factor(c_p)), alpha = .5, size = 2) + 
  scale_y_continuous(breaks = c(.001, .05, .5, 1), trans = scales::modulus_trans(-7, offset = 1)) +
  facet_wrap(~variable) +
  coord_cartesian(ylim = c(0.0001,.5)) +
  theme_minimal() +
  labs(title = 'reform = NA, boottype = parametric',
       x = 'Size of largest non-zero path (a or b)',
       y = 'Proportion false positive\n(95% CI)')
```

## Table of FPs

```{r}
knitr::kable(boot_sim_results_summary_l)
```

## Table of Bias

```{r}
knitr::kable(boot_sim_bias_summary)
```
